Enhancing Autonomy of Mobile Robots with Behavioral Tree using ROS2

### 2023-01-31 Paper/paper.tex
changed figure in paper

\begin{figure*}[ht]
	\centering
	\includegraphics[width=0.9\linewidth]{Figures/simplified_bt_inverted.png}
	\caption{Top Level Behavior Tree Structure}
	\label{fig:top_level_bt}
\end{figure*}

@@

The ROSBot robot requires several crucial modules to be developed for successful real-world experiments. One such module is the battery monitoring module, which is responsible for monitoring the battery level and providing updates to the rest of the system. This is crucial as it ensures the robot operates safely within its battery capacity and prevents unexpected power-off during operation. Another important module is the collision detection module, which helps the robot detect obstacles in its environment and respond accordingly. This module is essential for the robot's safety as it prevents damage to itself or other actors in the environment. The development of these modules is essential for ensuring the ROSBot's robustness and safe operation in real-world scenarios.

>>>>

\begin{figure*}[ht]
	\centering
	\includegraphics[width=0.9\linewidth]{Figures/top_level_bt.png}
	\caption{Top Level Behavior Tree Structure}
	\label{fig:top_level_bt}
\end{figure*}

@@

The ROSBot 2.0 by Husarion has been selected as the test platform for real world scenarios. It is a four-wheeled robot equipped with a suite of sensors, including LiDAR, IMU, wheel encoders and range sensors. To advance the ROSBot to a higher level of autonomy the proposed system architecture has been implemented. The battery charge module and the collision detection module were required to be adapated from the simulation to function on the real robot. The collision detection module is based on the IMU data instead of a simulated bumper sensor. The battery module estimates the remaining charge by taking the battery voltage, the power consumption of every component and the movement of the robot into account thus assuring that the robot has enough charge left to navigate to a goal.

% The ROSBot robot requires several crucial modules to be developed for successful real-world experiments. One such module is the battery monitoring module, which is responsible for monitoring the battery level and providing updates to the rest of the system. This is crucial as it ensures the robot operates safely within its battery capacity and prevents unexpected power-off during operation. Another important module is the collision detection module, which helps the robot detect obstacles in its environment and respond accordingly. This module is essential for the robot's safety as it prevents damage to itself or other actors in the environment. The development of these modules is essential for ensuring the ROSBot's robustness and safe operation in real-world scenarios.
